\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=2cm]{geometry}
\linespread{1.0}
\usepackage[english]{babel}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{changepage}

\pagestyle{empty}

% Section formatting: bold small caps with horizontal rule
\usepackage{titlesec}
\titleformat{\section}{\normalsize\bfseries\scshape}{}{0pt}{}[\vspace{2pt}\titlerule]
\titlespacing{\section}{0pt}{10pt}{4pt}

% For the diamond separator
\newcommand{\sep}{\ensuremath{\diamond}}

% Indent for section content
\newlength{\cvindent}
\setlength{\cvindent}{1em}

% Environment for indented section content
\newenvironment{cvbody}{%
  \begin{adjustwidth}{\cvindent}{}%
  \setlength{\parindent}{0pt}%
}{%
  \end{adjustwidth}%
}

\begin{document}

\begin{center}
    {\Large \textbf{ASKER NYGAARD CHRISTENSEN}\footnote{I am getting married in October 2026, so future publications will be under the name Asker Nygaard David.}} \\[0.15cm]
    {\small Last updated: March 2026. \href{https://askernc.github.io}{\underline{Website.}}}   \\[0.1cm]
    {\small Department of Economics, University of Copenhagen \quad \sep \quad \href{mailto:hms467@econ.ku.dk}{hms467@econ.ku.dk}}
\end{center}
%%%%%%%%%%%%%%%%%%%%

%%% TO COMILE AND ADD TO WEBISTE RUN bash cv/build.sh

%%%%%%%%%%%%%%%%%%%%%%


\section{Current Position}
\begin{cvbody}
\textbf{PhD Student} \hfill 2022-2026 \\
Department of Economics, University of Copenhagen

\end{cvbody}
\section{Affiliations}
\begin{cvbody}
The Danish Agency for Labour Market and Recruitment (STAR) \hfill 2022-2026
\end{cvbody}

\section{Education}
\begin{cvbody}
\textbf{PhD in Economics (4+4 programme)} \hfill 2022-2026\textsuperscript{*} \\
University of Copenhagen \\
{\small \textsuperscript{*}Handing in: June 2026}

\medskip

\textbf{Visiting PhD Student} \hfill fall 2024-spring 2025 \\
Cornell University

\medskip
\textbf{MSc in Economics} \hfill 2021-2024 \\
University of Copenhagen \\
{\small Obtained as part of the 4+4 programme}

\medskip
\textbf{BSc in Economics} \hfill 2017-2020 \\
University of Copenhagen
\end{cvbody}

\section{Publications}

\subsection*{\normalsize Peer-Reviewed Journal Articles}
\begin{cvbody}
\begin{itemize}[leftmargin=1.5em, labelsep=0.5em, itemsep=4pt, parsep=0pt]
    \item Arnarson, B.~T., \textbf{A.~N.~Christensen}, B.~S.~Javorcik and J.~R.~Munch. ``Globalisation and the Gender Gap in Mental Well-Being.'' Conditionally accepted, \textit{Journal of International Economics}.
\end{itemize}
\end{cvbody}

\subsection*{\normalsize Peer-Reviewed Working Papers}
\begin{cvbody}
\begin{itemize}[leftmargin=1.5em, labelsep=0.5em, itemsep=4pt, parsep=0pt]
    \item \textbf{A.~N.~Christensen}, N.~A.~Harmon, S.~Settele and D.~Skandalis. 2026. ``Relative Wage Misperceptions and Early Career Job Search.'' ROCKWOOL Fonden, Study Paper No.~279.
\end{itemize}
\end{cvbody}

\subsection*{\normalsize Peer-Reviewed Book Contributions}
\begin{cvbody}
\begin{itemize}[leftmargin=1.5em, labelsep=0.5em, itemsep=4pt, parsep=0pt]
    \item Munch, J.~R., B.~T.~Arnarson, \textbf{A.~N.~Christensen}, D.~H\'emous, A.~Humlum, B.~Javorcik, B.~B.~Meyer, M.~Olsen, P.~Plato, M.~Rasmussen and E.~Vestergaard, \textit{Omstilling p\aa{} Arbejdsmarkedet -- Globalisering, Automatisering og Uddannelse}. ROCKWOOL Fondens Forskningsenhed og Syddansk Universitetsforlag.
\end{itemize}
\end{cvbody}

\section{Previous Employment}
\begin{cvbody}
\textbf{Research Assistant}, University of Copenhagen \hfill 2019-2022 \\
Under the supervision of Prof.\ Jakob Roland Munch \\
{\small Data processing and analysis using Danish administrative register data on topics in international, labour, and gender economics.}

\medskip
\textbf{Student Assistant}, Dansk Energi \hfill 2018-2019
\end{cvbody}

\section{Research Interests}
\begin{cvbody}
My research interests are in labour economics and applied microeconometrics with a particular focus on job search, information frictions, gender economics, and text analysis/NLP methods applied to labour market data.

\smallskip
\textbf{Keywords}: Labour Economics, Applied Microeconometrics, Job Search, Text Analysis/NLP
\end{cvbody}

\section{Teaching Experience}
\begin{cvbody}
\textbf{Co-lecturer} \hfill spring 2023, 2024 \\
Introduction to Programming and Numerical Analysis, UCPH

\medskip
\textbf{Teaching Assistant} \hfill spring 2020, 2021 \\
Introduction to Programming and Numerical Analysis, UCPH
\end{cvbody}

\section{Conferences \& Presentations}

\subsection*{\normalsize Conference Presentations with Peer-Reviewed Admission}
\begin{cvbody}
\begin{itemize}[leftmargin=1.5em, labelsep=0.5em, itemsep=4pt, parsep=0pt]
    \item \textbf{2025}: European Economic Association Annual Congress, Bordeaux; European Society for Population Economics (ESPE).
    \item \textbf{2023}: Gender Gaps Conference, Warsaw (GRAPE).
\end{itemize}
\end{cvbody}

\subsection*{\normalsize Other Presentations}
\begin{cvbody}
\begin{itemize}[leftmargin=1.5em, labelsep=0.5em, itemsep=4pt, parsep=0pt]
    \item \textbf{2025}: PhD Seminar, University of Copenhagen; Copenhagen Workshop on Job Search and Micro Data, University of Copenhagen.
    \item \textbf{2024}: CoLab Seminar, University of Copenhagen; Labor Work-in-Progress Seminar, Cornell University; The Danish Agency for Labour Market and Recruitment (STAR); TWIPS, Cornell University.
    \item \textbf{2023}: Rockwool Foundation Research Unit.
    \item \textbf{2022}: Sardinian Empirical Trade Conference (F.R.E.I.T.) (Participant); Danish Graduate Program in Economics (DGPE) Workshop; CoLab Lunch Workshop, University of Copenhagen.
\end{itemize}
\end{cvbody}

\section{Grants \& Awards}
\begin{cvbody}
\textbf{2024}: Zeuthen Prize Nominee for best Master's Thesis in Economics. \textbf{Support for Cornell visit:} Flemming og Judy Heilmann stipendiet, Viet-Jacobsen, Rudolph Als Fondet, William Demant, Knud Højgaards fond, Augustinus Fonden.
\end{cvbody}

\section{Other Qualifications}
\begin{cvbody}
\textbf{Languages}: Danish (native), English (fluent) \\
\textbf{Programming}: Python (advanced), Stata (advanced), SAS (intermediate), Julia (intermediate)
\end{cvbody}

\end{document}
